\tool

### 2018-02-27 paper/paper.tex
Anonymize and fix headings

\documentclass[sigconf,review,anonymous]{acmart}
\acmConference[ESEC/FSE 2018]{The 26th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{4–9 November, 2018}{Lake Buena Vista, Florida, United States}
\usepackage{pdftexcmds}
%\usepackage[pdftex]{graphicx}
%\usepackage{multirow}
%\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
%\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{\textsl{tool-recommender-bot}}
\newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
\newcommand{\pseudosubsection}[1]{\vspace{2mm} \noindent{\it #1}}

@@

\section{Tool}
\tool aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our system for making recommendations similar to those from a peer and incorporating software engineering industry practices.

@@

To better understand what makes peer interactions an effective mode of tool discovery, our prior work observed how colleagues recommend tools to each other while working on tasks. Our results found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics, such as politeness and persuasiveness, do not significantly impact the outcome~\cite{vlhcc17}. We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.

\pseudosubsection{Receptiveness}

Previous work emphasizes the importance of receptivity. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. Our prior work defined receptiveness using two criteria introduced by Fogg: 1) demonstrating a desire and 2) familiarity with the target behavior and technology. Below we explain how \tool~was designed to recommend programming tools to software developers based on their desire and familiarity. \\

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. We aim to increase tool discovery by recommending software engineering tools designed to improve software quality. \\

@@

\pseudosubsection{Continuous Integration}

@@

\pseudosubsection{Fix Identification}

@@

\pseudosubsection{Code Review}

@@

\pseudosubsection{RQ1}

@@

\pseudosubsection{RQ2}

>>>>

\documentclass[sigconf,review,anonymous]{acmart}
\acmConference[ESEC/FSE 2018]{The 26th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{4–9 November, 2018}{Lake Buena Vista, Florida, United States}
\usepackage{pdftexcmds}
%\usepackage[pdftex]{graphicx}
%\usepackage{multirow}
%\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
%\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{\textsl{tool-recommender-bot}}

@@

\section{Tool}
\tool~aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our system for making recommendations similar to those from a peer and incorporating software engineering industry practices.

@@

To better understand what makes peer interactions an effective mode of tool discovery, prior work by Brown and colleagues observed how software users recommend tools to each other while completing tasks. They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation while other characteristics, such as politeness and persuasiveness, do not significantly impact recommendation outcome~\cite{vlhcc17}. We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.

Previous work emphasizes the importance of receptiveness. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. We define receptiveness using two criteria outlined by Fogg: 1) demonstrating desire and 2) familiarity with target behavior. Below we explain how we designed \tool~to recommend programming tools to software developers based on their desire and familiarity.

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. We aim to increase tool discovery by recommending software engineering tools designed to improve software quality.

@@

\subsubsection{Continuous Integration}

@@

\subsubsection{Fix Identification}

@@

\subsubsection{Code Review}

@@

\subsubsection{RQ1}

@@

\subsubsection{RQ2}
